Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-20 analysis/paper/paper.Rmd
Update findings of analysis

When predicting the availability of data availability as compared with *Phytopathology*, publications in three journals, *Crop Protection*, *Plant Disease* and *Revista Mexicana de Fitopatología*, can be considered clearly less likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title.
The effect of *Crop Protection* (Median = -2.13, 95% CI [-4.15, -0.59]) had a 99.78% probability of being negative (< 0), 99.70% of being significant (< -0.05), and 99.16% of being large (< -0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 19427).
The effect of *Plant Disease* (Median = -2.13, 95% CI [-4.14, -0.60]) had a 99.84% probability of being negative (< 0), 99.80% of being significant (< -0.05), and 99.15% of being large (< -0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 22687).
The effect of *Revista Mexicana Fitopatologia* (Median = -2.03, 95% CI [-4.09, -0.43]) had a 99.52% probability of being negative (< 0), 99.38% of being significant (< -0.05), and 98.38% of being large (< -0.30).
The estimation successfully converged (Rhat = 1.002) and the indices are reliable (ESS = 5769).

There was no effect detected for year when predicting the availability of computational methods (code) availability.
However, the effect of the publication year of 2016 on the availability of data (Median = 1.13, 95% CI [0.23, 2.05]) had a 99.27% probability of being positive (> 0), 99.08% of being significant (> 0.05), and 96.48% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 10707).
There was no detectable pattern in increasing or decreasing availability of data in the years examined.

There were no detectable effects when predicting the effects of the five-year impact factor on the availability of code or data.

No journals surveyed were completely closed, all offered at least an option for open access articles but `r rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()` (`r round(rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()/nrow(rrpp), 2)`%) were completely open.

>>>>

When predicting the availability of data availability as compared with *Phytopathology*, publications in two journals, *Phytopathologia Mediterrania* and *Molecular Plant Pathology*, can be considered clearly more likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title.
The effect of *Molecular Plant Microbe Interactions* (Median = 0.67, 95% CI [-0.28, 1.57]) has a 92.15% probability of being positive (> 0), 90.61% of being significant (> 0.05), and 78.94% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 25478).
The effect of *Phytopathologia Mediterranea* (Median = 1.25, 95% CI [0.32, 2.15]) has a 99.58% probability of being positive (> 0), 99.42% of being significant (> 0.05), and 97.73% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 24986).

There was no effect detected for year when predicting the availability of computational methods (code) or data availability.

There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data.
